Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains\\

### 2021-10-25 Article/main.tex
Added main talking points

\IEEEauthorblockN{Günther Drevin}
\IEEEauthorblockA{\textit{School of Computer Science and Information Systems} \\
\textit{North-West University,}\\
Potchefstroom, South Africa \\
\href{mailto:Gunther.Drevin@nwu.ac.za}{Gunther.Drevin@nwu.ac.za}}

@@

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

@@

\section{Ease of Use}

>>>>

\IEEEauthorblockN{Günther Drevin (Supervisor)}
\IEEEauthorblockA{\textit{School of Computer Science and Information Systems} \\
\textit{North-West University,}\\
Potchefstroom, South Africa \\
\href{mailto:Gunther.Drevin@nwu.ac.za}{Gunther.Drevin@nwu.ac.za}}

@@

\begin{abstract}
Education as a whole has seen no major improvements for a long period of time while society has matured and grown rapidly in the same time frame. Due to this teaching and learning methods can be seen as stale to certain students. One way to solve this issue is with the implementation of some from of the technology that has developed over the years. This study looks at the possibility of adapting various domains of knowledge into digital games referred to as Serious Games. The implementation of serious games within teaching may help keep certain students engaged with the content being presented and create further interest in the topic. However, before reaching this stage the means to transform these knowledge domains into a serious games must be studied. This is done by focusing on three fields in particular, those being Gamification, Ludology and Pedagogy.
\end{abstract}

\begin{IEEEkeywords}
Education, Gamification, Knowledge Domains, Ludology, Pedagogy, Serious Games
\end{IEEEkeywords}

@@

\section{Literature Review}
\subsection{Serious Games and Ludology}
\subsection{A Pedagogical Approach}
\subsection{Gamification and the Knowledge Domains}

\section{Methodology}
The following steps were taken to determine how serious games can be used for the various knowledge domains:

\begin{itemize}
\item[1.] Literature surrounding the applicable fields was researched
\item[2.] Case studies concerning serious games was studied and similarities noted
\item[3.] Select theories that aid this process were pinpointed
\item[4.] From this research, recommendations for the knowledge domains were made
\end{itemize}

\subsection{Sampling of Literature}
\subsection{Collection of Case Studies and Determine Similarities}
\subsection{Pinpointing Connected Theories}
\subsection{Extrapolate to other Knowledge Domains}

\section{Findings}
\subsection{Helpful Teaching Theories}
\subsection{Case Studies and the Similarities in Design Principles}

\section{Synthesis from Research}
\subsection{Recommendations per Knowledge Domain}
\subsection{Limitations and Future Research}
